Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
ok
Rmd update

## Introduction (MT + JM voi jo kasata tähän hyvää läppää + viitteitä)

@@

@@

>>>>

## Introduction

@@

The most active known female authors based on the title count:

```{r 201606krakow-fennica-topfemale, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=10}

theme_set(theme_bw(20))
dfs <- fen %>% filter(author_gender == "female")
p <- top_plot(dfs, "author", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count")
p <- p + ggtitle("Top female authors (Fennica)")
p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
pf = p

theme_set(theme_bw(20))
dfs <- kun %>% filter(author_gender == "female")
p <- top_plot(dfs, "author", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count")
p <- p + ggtitle("Top female authors (Kungliga)")
p <- p + theme(axis.text.x = element_text(size = 16), axis.text.y = element_text(size = 16), axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 22), title = element_text(size = 22))
pk = p

library(gridExtra)
grid.arrange(pf, pk, nrow = 1)
```

The top publication places ranked by the title count

```{r LIBER-topplace, echo=FALSE, message=FALSE, cache=FALSE, fig.height=6, fig.width=6}
theme_set(theme_bw(30))
p <- top_plot(fen, "publication_place", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count (Log10 scale)")
p <- p + scale_y_log10()
p <- p + ggtitle("Top publication places (Fennica)")
pf = p

theme_set(theme_bw(30))
p <- top_plot(kun, "publication_place", ntop = 20)
p <- p + scale_fill_manual(values = "black")
p <- p + guides(fill = "none")
p <- p + ylab("Title count (Log10 scale)")
p <- p + scale_y_log10()
p <- p + ggtitle("Top publication places (Kungliga)")
pk = p

grid.arrange(pf, pk, nrow = 1)
```

Title count and overall paper consumption in the top publication locations (Fennica). The current country of origin is indicated. Finland is highlighted. Note that paper consumption estimates have still problems.

```{r LIBER-8, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=8}
df <- fen
theme_set(theme_bw(20))
top <- names(rev(sort(table(df$publication_place))))[1:50]
dfs <- df %>% filter(publication_place %in% top) %>% group_by(publication_place) %>% summarize(titles = n(), paper = sum(paper.consumption.km2, na.rm = T))
dfs$country <- get_country(dfs$publication_place)
dfs$finland <- dfs$country == "Finland"
p <- ggplot(dfs, aes(x = titles, y = paper))
p <- p + geom_text(aes(label = publication_place, color = finland), size = 5)
p <- p + xlab("Title Count") + ylab("Paper consumption (km2)")
p <- p + scale_color_manual(values = c("darkgray", "black"))
p <- p + guides(color = "none")
p <- p + scale_x_log10() + scale_y_log10() 
p <- p + ggtitle("Title count versus paper (places)")
print(p)	 
```

Gatherings vs. pagecounts per country (Fennica)

```{r LIBER-docsizecomp3, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
dfs <- fen %>% select(pagecount, gatherings, country) %>% filter(country %in% selected.countries) %>% group_by(pagecount, gatherings, country) %>% tally()
p <- ggplot(dfs, aes(x = pagecount, y = gatherings, size = n)) +
     geom_point() + facet_grid(country ~ .) + scale_x_log10()
print(p)
```

Average paper consumption per document

```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
theme_set(theme_bw(25))
library(sorvi)
df = df.preprocessed
dfs <- df %>% group_by(publication_year) %>%
         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
       geom_line() + geom_point() +
       xlab("Publication Year") + ylab("Paper per document")
p <- p + ggtitle("Average paper consumption per document")
print(p)
```

Paper consumption in books (balls) versus pamphlets (triangles). Books are any documents with more than 32 pages. Pamphlets are anything less or equal than 32 pages. Fennica data

```{r LIBER-12, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=6, fig.width=12}
df2 <- fen
df2$document.type <- rep(NA, nrow(df2))
df2$document.type[df2$pagecount > 32] <- "book"
df2$document.type[df2$pagecount <= 32] <- "pamphlet"
df2 <- df2[which(!is.na(df2$document.type)),]
df2$document.type <- factor(df2$document.type)
df2 <- df2 %>% group_by(publication_decade, document.type) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
p <- ggplot(df2, aes(x = publication_decade, y = paper.consumption.km2, group = document.type))
p <- p + geom_point(aes(shape = document.type), size = 5)
p <- p + geom_smooth(method = "loess", color = "black")
p <- p + ggtitle("Paper consumption per document type")
p <- p + xlab("Year")
p <- p + ylab("Paper consumption (km2)")
p <- p + scale_color_manual(values=c("black", "darkgray"))
p <- p + guides(shape = "none")
p <- p + ggtitle("Books versus pamphlets: paper consumption")
print(p)
```

Paper consumption for different document formats over time. Each point represents a decade. Loess smoothing. Fennica.

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6}
df2 <- df %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
p <- p + geom_point(size = 4)
p <- p + geom_smooth(method = "loess", size = 1, color = "black")
p <- p + ggtitle("Paper consumption in time by gatherings")
p <- p + xlab("Year")
p <- p + ylab("Paper consumption (km2)")
p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
p <- p + ggtitle("Paper consumption for different document formats")
print(p)
```

@@

## Session info

This document was created with the following versions:

```{r sessioninfo, message=FALSE, warning=FALSE}
sessionInfo()
```
